Inaction on climate change projected to cost one year of life in some European

### 2018-10-23 supplementary_rcode.Rmd
minor edits.

---
title: "Climate Change Projected to Reduce European Life Expectancy"
output:
  word_document: default
  pdf_document: default
date: "April 5, 2018"
---

@@

To successfully run this code, several R pacakgse must be installed and these
packages are located just below this text section but are tidyverse, HMHFDplus,
tmap, tmaptools, RColorBrewer, data.table, and getPass.

>>>>

---
title: Inaction on climate change projected to cost one year of life in some European
  countries
output:
  html_document:
    df_print: paged
  pdf_document: default
  word_document: default
date: "October 19, 2018"
---

@@

To successfully run this code, several R packages must be installed and these
packages are located just below this text section but are tidyverse, HMHFDplus,
tmap, tmaptools, RColorBrewer, data.table, and getPass.
